### 2018-07-16 FrascatiPlot/Paper/NucleiB2.tex
Version for submission to the arXiv: all figures in png format, comments removed -- it compiles properly on arXiv! :)
Fixed last couple of issues, added emails, removed reference to r = 0.3 fm from thermal model, .... and finally we are good to go

\usepackage{lineno}
\linenumbers

@@

F. Bellini$^{1}$ and A. Kalweit$^{1}$
\\$^{1}$CERN, Switzerland
\medskip

15th July 2018
\end{center}

@@

\begin{equation}
\langle C_{d} \rangle \approx \frac{1}{\left[1+ \left(\frac{\dradius}{2R_{\perp}(m_{T})}\right)^{2}\right] \sqrt{1+ \left(\frac{\dradius}{2R_{\|}(m_{T})}\right)^{2}}}
\label{eq:Cd}
\end{equation}
%
where \dradius~is the radius of the deuteron, \rperp~and \rpar~are the lengths of homogeneity of the coalescence volume and $m_{T}$ is the transverse mass of the coalescing nucleons.
The size of the nucleus enters in the determination of the coalescence parameter \btwo~via the quantum-mechanical correction factor $\langle C_{d} \rangle$, as well as the homogeneity volume $\rperp^{2}\rpar$, according to the relation
%
\begin{equation}
\btwo = \frac{3\pi^{3/2} \langle C_{d} \rangle}{2m_{T}\rperp^{2}(m_{T})\rpar(m_{T})}
\label{eq:B2cd}
\end{equation}
%
which is the main result of \cite{Scheibl:1998tk}. It is interesting to note that the coalescence parameter decreases with increasing volume, as expected. In addition to this, the quantum mechanical correction factor introduces a length scale defined by the deuteron size relative to the source size in the calculation of \btwo, which reflects the coalescence probability. 
If we assume that  $\rperp \approx \rpar \approx R$, Eqs. \ref{eq:Cd} and \ref{eq:B2cd} simplify to 
\begin{equation}
\langle C_{d} \rangle \approx \left[1+ \left(\frac{\dradius}{2R(m_{T})}\right)^{2}\right]^{-3/2}
\label{eq:Cdapprox}
\end{equation}
%
and
%
\begin{equation}
\btwo = \frac{3\pi^{3/2} \langle C_{d} \rangle}{2m_{T}R^{3}(m_{T})}.
\label{eq:B2approx}
\end{equation}
%
Figure \ref{fig:radiusDependence} shows the source radius ($R$) dependence of the quantum-mechanical correction factor (on the left) and the coalescence parameter \btwo~(on the right), calculated assuming (a.) a point-like nucleus $\dradius = 0$, (b.) $\dradius = 0.3$ fm, similar to the value currently assumed in thermal model calculations \cite{Andronic:2016nof}, (c.) the actual value which reproduces the measured rms radius of the deuteron $\dradius = 3.2$ fm \cite{Mohr:2015ccw}, (d.) a larger, irrealistic value of  $\dradius = 10$ fm. 
As can be seen in Fig. \ref{fig:radiusDependence}, the quantum-mechanical correction factor leads to a significant suppression in the production of those objects whose radius is large compared to that of the source.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.0\textwidth]{theory_coalescence_Cd_B2.eps}
\caption{{The quantum mechanical correction factor $\langle C_{d} \rangle$ (left panel, see Eq. \ref{eq:Cdapprox}) and the coalescence parameter \btwo~for deuteron (right panel, see Eq. \ref{eq:B2approx}) as a function of the radius of the source, $R$, calculated assuming a size parameter for the deuteron $\dradius = 0, 0.3, 3.2$ and $10$ fm.}}
\label{fig:radiusDependence}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.7\textwidth]{HbtRadiusParam.eps}
\caption{Parameterisation of the dependence of the source radius on multiplicity assumed in this paper, compared to HBT data from \cite{Adam:2015vna, Adam:2015pya, Abelev:2012sq}. The radius $R$ and the parameters $a$ and $b$ are in units of fm.}
\label{fig:radiiparam}
\end{center}
\end{figure}

@@

In the statistical-thermal approach, the yields (d$N$/d$y$) of light anti- and hyper-nuclei are very sensitive to the chemical freeze-out temperature $T_{chem}$ due to their large mass $m$ and approximately scale as d$N$/d$y \propto \exp(-m/T_{chem})$. As a matter of fact, the chemical freeze-out temperature defines the only scale in this model, since at the LHC the chemical potentials which ensure the conservation of baryon number ($\mu_{B}$), strangeness ($\mu_{S}$), and electric charge ($\mu_{Q}$) are negligible.
In contrast to the coalescence approach, the current implementations~\cite{Petran:2013dva,Wheaton:2004qb,Andronic:2005yp} of the statistical-thermal model provide only \pt-integrated yields and not the \pt-differential hadron spectra. 
In order to fill this gap, and for the purposes of this exercise, \pt~spectra have been modelled using a blast-wave~\cite{Schnedermann:1993ws} parameterization. When extracting the predicted spectrum for a given particle species (proton, $\Lambda$, deuteron, \hethree), the parameters of the blast-wave (average radial flow velocity $\langle\beta_{T}\rangle$, kinetic freeze-out temperature $T_{kin}$, and velocity profile $n$) are fixed to the values obtained from the simultaneous fit to the pion, kaon and proton spectra measured in Pb--Pb collisions as a function of centrality by ALICE~\cite{Abelev:2013vea}. 
The normalisation is fixed using the \pt-integrated deuteron-to-pion ratio and \hethree-to-pion ratio predicted by the GSI-Heidelberg model with $T_{chem} = 156$ MeV, multiplied by the pion yield measured by ALICE~\cite{Abelev:2013vea}. 
This choice, as opposed to using ratio to proton, is motivated by the fact that the measured proton yield is seen to be slightly underestimated by the thermal model predictions at the LHC~\cite{Abelev:2012wca}.
In the case of hyper-triton, a slightly different procedure is chosen, namely the normalisation for \hthreelambda~is extracted from the statistical-thermal model prediction of the strangeness population factor $S_{3}$ multiplied by the measured $\Lambda/p$ ratio~\cite{Abelev:2013vea,Abelev:2013xaa} and the measured \hethree~yield~\cite{ALICE:deuteronppPbPb2015}. Based on the spectra obtained in this way, we calculate the corresponding coalescence parameters for a given \pt/$A$ and compare it with coalescence expectations. Because we use experimental data to constrain the blast-wave prediction as well as the normalisation, and because such data are provided for given centrality classes, we use the corresponding \avdNdeta~in each class to estimate the system radius based on the parameterisation discussed in Sec.~\ref{SecSourceVolume}. 
In contrast to the coalescence approach, which explicitly depends on the size of the produced object with respect to the system size, the object size does not enter in the formulation of the blast-wave model. Being a simplified hydrodynamic model, the latter treats the system as a continuum and is not particle based. The thermal model on the other hand, implements eigenvolume corrections by fixing the object radius as an external parameter ($r=0.3$~fm in the case of baryons for the GSI-Heidelberg model used here). We refer to the literature for the extensive discussions on the validity of the eigenvolume correction for light anti- and hyper-nuclei~\cite{Vovchenko:2016mwg} and the relation with the possible production of these objects as compact quark bags~\cite{Andronic:2017}.

@@

Data on anti- and hyper-nuclei production at LHC energies and different collision systems have been released by the ALICE Collaboration in recent years \cite{ALICE:nucleipp2017,ALICE:deuteronppPbPb2015,Acharya:2017dmc, Adam:2015yta}. 
In Fig. \ref{fig:CompareB2B3forDifferentParamWithData} we compare the coalescence parameter for deuteron (\btwo) from the coalescence model (see Eqs.~\ref{eq:B2cd} and \ref{eq:B2approx}, with $r_{d} = 3.2$ fm) to the ALICE data for Pb-Pb collisions at $\sqrt{s_{\mathrm{NN}}} = 2.76$ TeV and pp collisions at $\sqrt{s} = 7$ TeV. For pp collisions, data in  \cite{ALICE:nucleipp2017} are given for inelastic (INEL) collisions. In order to facilitate the comparison with future multiplicity-dependent data given in the INEL$>0$ class, we have rescaled the \btwo~and \bthree~by the ratio of the charged particle multiplicity density in these two event classes \cite{Adam:2015gka}.
First, the parameterisation of the system radius fitted to the HBT data as described in Sec.~\ref{SecSourceVolume} (labeled in the following as "parameterisation A") is used to map the \avdNdeta~to the source size (top left panel of Fig. \ref{fig:CompareB2B3forDifferentParamWithData}). 
We notice already at this point that the coalescence volume from parameterisation A radii leads to discrepancies with respect to the curve from the coalescence calculation, and in particular, we notice that the model would require a larger radius for a given value of \btwo~for Pb-Pb collisions.

@@

\begin{figure}[ht]
	\begin{center}
		\includegraphics[width=0.8\textwidth]{compareThermalAndCoalescence.png}
		\caption{Comparison of the coalescence parameters measured by ALICE (solid markers) for deuterons (upper left panel), \hethree\ (lower left panel) and \hthreelambda\ (lower right panel) in pp \cite{ALICE:nucleipp2017} and Pb--Pb~\cite{ALICE:deuteronppPbPb2015, Adam:2015yta} collisions with the thermal+BW model expectations (dotted line) and the coalescence predictions (solid lines). Parameterisation B has been used to map the charged particle multiplicity density into the radius $R$ of the source (see text for details). The dashed line in the lower right panel corresponds to the coalescence prediction for the \hthreelambda\ with a larger radius.}
		\label{fig:CompareThermalAndCoalescence}
	\end{center}
\end{figure}

@@

\newenvironment{acknowledgement}{\relax}{\relax}
\begin{acknowledgement}
\section*{Acknowledgements}
We thank U. Heinz for the useful discussions and the clarification on the equivalence of the Bertsch-Pratt and Yano-Koonin-Podgoretskii parameterisations of the HBT radii. We further acknowledge discussions with Benjamin Doenigus, in particular about the production of \hthreelambda\ in pp collisions. In addition, we would like to thank Juergen Schukraft, Peter Braun-Munzinger, Roman Lietava, Kfir Blum and the colleagues from the ALICE Collaboration for their valuable input.

\end{acknowledgement}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% A = 4 Appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{RMS of a gaussian wave-function for A=4 }\label{appendix:integration}

In this appendix, we show the calculation of the RMS of a gaussian wave-function with the example of A=4. We start from the wave-function

>>>>

\usepackage{lineno}
%\linenumbers

@@

F. Bellini and A. Kalweit \footnote{Contacts: fbellini@cern.ch, akalweit@cern.ch}
\\CERN, EP Department, Geneva (Switzerland)

16$^{th}$ July 2018
\end{center}

@@

\begin{equation}
\langle C_{d} \rangle \approx \frac{1}{\left[1+ \left(\frac{\dradius}{2R_{\perp}(m_{T})}\right)^{2}\right] \sqrt{1+ \left(\frac{\dradius}{2R_{\|}(m_{T})}\right)^{2}}}
\label{eq:Cd}
\end{equation}
%
where \dradius~is the radius of the deuteron, \rperp~and \rpar~are the lengths of homogeneity of the coalescence volume and $m_{T}$ is the transverse mass of the coalescing nucleons.
The size of the nucleus enters in the determination of the coalescence parameter \btwo~via the quantum-mechanical correction factor $\langle C_{d} \rangle$, as well as the homogeneity volume $\rperp^{2}\rpar$, according to the relation
%
\begin{equation}
\btwo = \frac{3\pi^{3/2} \langle C_{d} \rangle}{2m_{T}\rperp^{2}(m_{T})\rpar(m_{T})}
\label{eq:B2cd}
\end{equation}
%
which is the main result of \cite{Scheibl:1998tk}. It is interesting to note that the coalescence parameter decreases with increasing volume, as expected. In addition to this, the quantum mechanical correction factor introduces a length scale defined by the deuteron size relative to the source size in the calculation of \btwo, which reflects the coalescence probability. 
If we assume that  $\rperp \approx \rpar \approx R$, Eqs. \ref{eq:Cd} and \ref{eq:B2cd} simplify to 
\begin{equation}
\langle C_{d} \rangle \approx \left[1+ \left(\frac{\dradius}{2R(m_{T})}\right)^{2}\right]^{-3/2}
\label{eq:Cdapprox}
\end{equation}
%
and
%
\begin{equation}
\btwo = \frac{3\pi^{3/2} \langle C_{d} \rangle}{2m_{T}R^{3}(m_{T})}.
\label{eq:B2approx}
\end{equation}
%
Figure \ref{fig:radiusDependence} shows the source radius ($R$) dependence of the quantum-mechanical correction factor (on the left) and the coalescence parameter \btwo~(on the right), calculated assuming (a.) a point-like nucleus $\dradius = 0$, (b.) $\dradius = 0.3$ fm, (c.) the actual value which reproduces the measured rms radius of the deuteron $\dradius = 3.2$ fm \cite{Mohr:2015ccw}, (d.) a larger, irrealistic value of  $\dradius = 10$ fm. 
As can be seen in Fig. \ref{fig:radiusDependence}, the quantum-mechanical correction factor leads to a significant suppression in the production of those objects whose radius is large compared to that of the source.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.0\textwidth]{theory_coalescence_Cd_B2.png}
\caption{{The quantum mechanical correction factor $\langle C_{d} \rangle$ (left panel, see Eq. \ref{eq:Cdapprox}) and the coalescence parameter \btwo~for deuteron (right panel, see Eq. \ref{eq:B2approx}) as a function of the radius of the source, $R$, calculated assuming a size parameter for the deuteron $\dradius = 0, 0.3, 3.2$ and $10$ fm.}}
\label{fig:radiusDependence}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.7\textwidth]{HbtRadiusParam.png}
\caption{Parameterisation of the dependence of the source radius on multiplicity assumed in this paper, compared to HBT data from \cite{Adam:2015vna, Adam:2015pya, Abelev:2012sq}. The radius $R$ and the parameters $a$ and $b$ are in units of fm.}
\label{fig:radiiparam}
\end{center}
\end{figure}

@@

In the statistical-thermal approach, the yields (d$N$/d$y$) of light anti- and hyper-nuclei are very sensitive to the chemical freeze-out temperature $T_{chem}$ due to their large mass $m$ and approximately scale as d$N$/d$y \propto \exp(-m/T_{chem})$. As a matter of fact, the chemical freeze-out temperature defines the only scale in this model, since at the LHC the chemical potentials which ensure the conservation of baryon number ($\mu_{B}$), strangeness ($\mu_{S}$), and electric charge ($\mu_{Q}$) are negligible.
In contrast to the coalescence approach, the current implementations~\cite{Petran:2013dva,Wheaton:2004qb,Andronic:2005yp} of the statistical-thermal model provide only \pt-integrated yields and not the \pt-differential hadron spectra. 
In order to fill this gap, and for the purposes of this exercise, \pt~spectra have been modelled using a blast-wave~\cite{Schnedermann:1993ws} parameterization. When extracting the predicted spectrum for a given particle species (proton, $\Lambda$, deuteron, \hethree), the parameters of the blast-wave (average radial flow velocity $\langle\beta_{T}\rangle$, kinetic freeze-out temperature $T_{kin}$, and velocity profile $n$) are fixed to the values obtained from the simultaneous fit to the pion, kaon and proton spectra measured in Pb--Pb collisions as a function of centrality by ALICE~\cite{Abelev:2013vea}. 
The normalisation is fixed using the \pt-integrated deuteron-to-pion ratio and \hethree-to-pion ratio predicted by the GSI-Heidelberg model with $T_{chem} = 156$ MeV, multiplied by the pion yield measured by ALICE~\cite{Abelev:2013vea}. 
This choice, as opposed to using ratio to proton, is motivated by the fact that the measured proton yield is seen to be slightly underestimated by the thermal model predictions at the LHC~\cite{Abelev:2012wca}.
In the case of hyper-triton, a slightly different procedure is chosen, namely the normalisation for \hthreelambda~is extracted from the statistical-thermal model prediction of the strangeness population factor $S_{3}$ multiplied by the measured $\Lambda/p$ ratio~\cite{Abelev:2013vea,Abelev:2013xaa} and the measured \hethree~yield~\cite{ALICE:deuteronppPbPb2015}. Based on the spectra obtained in this way, we calculate the corresponding coalescence parameters for a given \pt/$A$ and compare it with coalescence expectations. Because we use experimental data to constrain the blast-wave prediction as well as the normalisation, and because such data are provided for given centrality classes, we use the corresponding \avdNdeta~in each class to estimate the system radius based on the parameterisation discussed in Sec.~\ref{SecSourceVolume}. 
In contrast to the coalescence approach, which explicitly depends on the size of the produced object with respect to the system size, the object size does not enter in the formulation of the blast-wave model. Being a simplified hydrodynamic model, the latter treats the system as a continuum and is not particle based. The thermal model on the other hand, implements eigenvolume corrections by fixing the object radius as an external parameter (0.3 fm in the case of baryons for the GSI-Heidelberg model used here). We refer to the literature for the extensive discussions on the validity of the eigenvolume correction for light anti- and hyper-nuclei~\cite{Vovchenko:2016mwg} and the relation with the possible production of these objects as compact quark bags~\cite{Andronic:2017}.

@@

Data on anti- and hyper-nuclei production at LHC energies and different collision systems have been released by the ALICE Collaboration in recent years \cite{ALICE:nucleipp2017,ALICE:deuteronppPbPb2015,Acharya:2017dmc, Adam:2015yta}. 
In Fig. \ref{fig:CompareB2B3forDifferentParamWithData} we compare the coalescence parameter for deuteron (\btwo) from the coalescence model (see Eqs.~\ref{eq:B2cd} and \ref{eq:B2approx}, with $r_{d} = 3.2$ fm) to the ALICE data for Pb-Pb collisions at $\sqrt{s_{\mathrm{NN}}} = 2.76$ TeV and pp collisions at $\sqrt{s} = 7$ TeV. For pp collisions, data in  \cite{ALICE:nucleipp2017} are given for inelastic (INEL) collisions. In order to facilitate the comparison with future multiplicity-dependent data given in the INEL$>$0 class, we have rescaled the \btwo~and \bthree~by the ratio of the charged particle multiplicity density in these two event classes \cite{Adam:2015gka}.
First, the parameterisation of the system radius fitted to the HBT data as described in Sec.~\ref{SecSourceVolume} (labeled in the following as "parameterisation A") is used to map the \avdNdeta~to the source size (top left panel of Fig. \ref{fig:CompareB2B3forDifferentParamWithData}). 
We notice already at this point that the coalescence volume from parameterisation A radii leads to discrepancies with respect to the curve from the coalescence calculation, and in particular, we notice that the model would require a larger radius for a given value of \btwo~for Pb-Pb collisions.

@@

\begin{figure}[ht]
	\begin{center}
		\includegraphics[width=\textwidth]{compareThermalAndCoalescence.png}
		\caption{Comparison of the coalescence parameters measured by ALICE (solid markers) for deuterons (upper left panel), \hethree\ (lower left panel) and \hthreelambda\ (lower right panel) in pp \cite{ALICE:nucleipp2017} and Pb--Pb~\cite{ALICE:deuteronppPbPb2015, Adam:2015yta} collisions with the thermal+BW model expectations (dotted line) and the coalescence predictions (solid lines). Parameterisation B has been used to map the charged particle multiplicity density into the radius $R$ of the source (see text for details). The dashed line in the lower right panel corresponds to the coalescence prediction for the \hthreelambda\ with a larger radius.}
		\label{fig:CompareThermalAndCoalescence}
	\end{center}
\end{figure}

@@

\newenvironment{acknowledgement}{\relax}{\relax}
\begin{acknowledgement}
\section*{Acknowledgements}
We would like to thank Kfir Blum for inspiring this work. We thank U. Heinz for the useful discussions and the clarification on the equivalence of the Bertsch-Pratt and Yano-Koonin-Podgoretskii parameterisations of the HBT radii. We further acknowledge discussions with Benjamin Doenigus, in particular about the production of \hthreelambda\ in pp collisions, and with Eulogio Serradilla Rodriguez. In addition, we would like to thank Juergen Schukraft, Peter Braun-Munzinger, Maximiliano Puccio, Roman Lietava and the colleagues from the ALICE Collaboration for their valuable input. 
\end{acknowledgement}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% A = 4 Appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{RMS of a gaussian wave-function for $\mathbf{A=4}$}\label{appendix:integration}

In this appendix, we show the calculation of the RMS of a gaussian wave-function with the example of $A=4$. We start from the wave-function
